\papertitle

### 2014-03-19 final-report/paper.tex
more intro

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool
is called \system, which uses profiling logs from Myria \cite{myria} as the prototype DDMS. Myria is a distributed 
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently, Myria does not offer a visualization tool designed to show the physical query plan, job execution and network 
communication between distributed workers. \system allows the programmer/database administrator to visualize the following aspects
of query execution.

@@

>>>>

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool
is called \system, which uses profiling logs from \emph{Myria} \cite{myria} as the prototype DDMS. Myria is a distributed 
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently, Myria does not offer a visualization tool designed to show the physical query plan, job execution and network 
communication between distributed workers. \system allows the programmer/database administrator to visualize the following aspects
of query execution.

@@

\item A view for cluster utilization and operator performance for each \emph{Myria} segment. Each segment is composed of
multiple sequential database operators running on the same worker. Upon clicking on a collapsed segment node in the
query plan DAG, the node expands to display the operators comprising the segment and renders the fragment execution view.
The fragment execution view visualizes the utilization of the cluster by showing whether each worker is busy working 
on the selected fragment. It also breaks down the work done by each worker into operators composing the fragment.
